### 2021-10-26 manuscript/manuscript.Rmd
Continue Methods section

>>>>

After familiarization, participants performed a series of trials envolving jumps of different types and heights. First, drop jumps were executed from steps varying from 5cm to 40cm high, with 5cm increments. Then, box jumps were performed from the floor to 5cm, 15cm and 30cm high boxes. Finally, continuous jumps were carried out in two different heights: 5cm and 15cm. Drop and box jumps were realized in two sets of four jumps at each height, with 30s interval, and the continuous jumps in one set of 20s at each height. The landing phase of the drop jumps, the take-off phase of the box jumps and both phases of the continuous jumps were recorded in force plates (1000Hz; AMTI Corporation, Watertown, USA). Participants were instructed to jump with no restrictions to arms movement, land two-footed and then remain stationary on the force plate for five seconds (except in the continuous jumps).

Throughout the protocol, three activity monitors (GT9X Link; 100Hz; ±16g range; ActiGraph, Pensacola, USA) were worn by each participant, at the following placements: i) at their right hip (along the anterior axillary line, at the level of the iliac crest); ii) at their lower back (at the midpoint between the two posterior superior iliac spines); and iii) at their right ankle (immediately superior to the lateral malleolus). Activity monitors at waist level were secured on the same elastic belt with a clip and the activity monitor placed on the ankle was secured by an elastic belt fixed with adhesive tape. In all placements, the accelerometer vertical axis was aligned with the standing body longitudinal axis.

The motion sensors used incorporate primary and secondary triaxial accelerometers. As the manufacturer proprietary filter is not applied on the secondary accelerometer raw data, to improve the data processing replicability only data from that accelerometer were used in this study. Data from FP and accelerometers were operated through the manufacturer supplied software (for the FP: Netforce, Version 3.5.1; AMTI Corporation, Watertown, USA; for the accelerometers: ActiLife version 6.13.3; Actigraph, Pensacola, USA) and exported as raw data from the *x*, *y* and *z* vectors. GRF was expressed in N and acceleration (ACC) in gravitational ACC units (1*g* = 9.807 m·s^-2^).

FP and accelerometer data were processed using MATLAB (Version 2019a, Mathworks, Natick, USA) according to the following procedures: first, both GRF and ACC signals were filtered using a Butterworth fourth-order low-pass filter, with 20 Hz cut-off frequency, to attenuate the noise magnitude. This cut-off frequency was selected based on visual inspection of the signals frequency spectrum after a Fast Fourier Transform (FFT). Afterwards, the GRF and ACC resultant vector was calculated ($r_i = \sqrt{x_i^2 + y_i^2 + z_i^2}$)
